Did COVID-19 Induce A Strenuous Effect on the 311 Non-Emergency Services System?

### 2022-07-15 draft_v2.Rmd
update

#combine reg 
screenreg(list(reg_fe_11, reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )

>>>>

#combine reg 
screenreg(list(reg_fe_11, reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Sidewalks / Curbs / Ditch", "Signs","Storm Water / Sewer","Streets / Roadways / Alleys","Trash / Recycling"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees"))
```

Departments

```{r cate_dept, fig.height=6,fig.width=8}
dat %>%
  filter(CATEGORY != "Data Not Available") %>%
  filter(CREATEMO %in% 3:8) %>%
  group_by(CATEGORY, DEPT) %>%
  count() %>%
  left_join(diff)%>%
  ggplot(aes(x = reorder(CATEGORY,-diff_pchg), y = DEPT, fill = n))+
  geom_tile(lwd=1.5)+
  scale_x_discrete(guide = guide_axis(angle = 90))+
  labs(
    y = "Department",
    x = "Category",
    fill = "Request Volume",
    col = "Selected Catgories"
  )+
  theme_bw()
```

```{r}
#fe: 911 + gov employees
reg_fe_01 = (felm(data = dat_reg[dat_reg$DEPT=="Aviation",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_02 = (felm(data = dat_reg[dat_reg$DEPT=="City Managers Office",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_03 = (felm(data = dat_reg[dat_reg$DEPT=="City Planning and Development",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
#reg_fe_04 = (felm(data = dat_reg[dat_reg$DEPT=="Convention and Entertainment Center",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_05 = (felm(data = dat_reg[dat_reg$DEPT=="Finance",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_06 = (felm(data = dat_reg[dat_reg$DEPT=="Fire",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_07 = (felm(data = dat_reg[dat_reg$DEPT=="General Service",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_08 = (felm(data = dat_reg[dat_reg$DEPT=="Health",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
#reg_fe_09 = (felm(data = dat_reg[dat_reg$DEPT=="KCPD",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_10 = (felm(data = dat_reg[dat_reg$DEPT=="NHS",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
#reg_fe_11 = (felm(data = dat_reg[dat_reg$DEPT=="Northeast",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_12 = (felm(data = dat_reg[dat_reg$DEPT=="Northland",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_13 = (felm(data = dat_reg[dat_reg$DEPT=="Parks and Rec",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_14 = (felm(data = dat_reg[dat_reg$DEPT=="Public Works",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_15 = (felm(data = dat_reg[dat_reg$DEPT=="South",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))
reg_fe_16 = (felm(data = dat_reg[dat_reg$DEPT=="Water Services",],DAYTOCLOSE~did+empgov+kcmo_fire_vol+kcmo_pd_vol|n_allcovid+after ))

#combine reg 
screenreg(list(reg_fe_01, reg_fe_02,reg_fe_03,reg_fe_05), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Aviation","City Managers Office","City Planning and Development","Finance"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )

#combine reg 
screenreg(list(reg_fe_06, reg_fe_07,reg_fe_08,reg_fe_10), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Fire","General Service","Health","NHS"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees")
          )

#combine reg 
screenreg(list(reg_fe_12,reg_fe_13,reg_fe_14,reg_fe_15,reg_fe_16), 
          omit.coef = "after|n_allcovid|Intercept|NEIGH", digits=4, 
          include.rsquared = FALSE, include.adjrs = FALSE, include.rmse = FALSE,
          custom.model.names = c("Northland","Parks and Rec","Public Works","South","Water Services"),
          custom.coef.names = c("DiD effect","911 Vol Fire Department","911 Vol Police Department","Local Government Employees"))
```
